---
type: "overview_page"
layout: "overview-static"
---

# Program Structure

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(kableExtra)
library(dplyr)
```

<div class="banner">
  
  <div class = "term"><p>4</p></div>
  <div class = "m orange show" target="1"><p>ME8:<br>Master Thesis<br>30 ECTS</p></div>

  <div class = "term"><p>3</p></div>
  <div class = "w yellow l show" target="2"><p>ME4:<br> Time Series Analysis<br>10 ECTS</p></div>
  <div class = "w red show" target="3"><p>ME6:<br>Applied Econometrics<br>11 - 25 ECTS</p></div>
  <div class = "w purple show" target="5"><p>ME5:<br>Economics<br>11 - 25 ECTS</p></div>
  
  <div class = "term"><p>2</p></div>
  <div class = "w yellow l show" target="8"><p>ME2:<br>Econometrics<br>10 ECTS</p></div>
  <div class = "red show" target="3"><p>ME6:<br>Applied Econometrics</p></div>
  <div class = "green show" target="6"><p>ME7:<br>Econometric Methods</p></div>
  <div class = "w yellow show" target="9"><p>ME3:<br>Case Studies<br>8 ECTS</p></div>
  
  <div class = "term"><p>1</p></div>
  <div class="wider yellow l show" target="7"><p>ME1:<br> Statistical Theory<br>15 ECTS</p></div>
  <div class = "w green show" target="6"><p>ME7:<br>Econometric Methods<br>11 - 25 ECTS</p></div>
  <div class = "purple show" target="5"><p>ME5:<br>Economics</p></div>
</div>

<div class="cont">
  <div class="sec" id="section1">
  <h3>ME8: Master Thesis</h3>
  <p class = "text_ml">
  The master thesis demonstrates that students are able to independently apply and adapt scientific methods to an econometric problem within a given period of time. The processing time is six months. Topics for final theses are offered each semester by several university lecturers, so that students can choose between different offers. Students can also make their own suggestions for topics.</p>
  </div>
  <div class="sec" id="section2">
  <h3>ME4: Time Series Analysis</h3>
  <p class = "text_ml">
  The course covers methods of descriptive time series analysis on the one hand. On the other hand structure theory and estimation of time series models are discussed. Possible topics are approximation and elimination of trends, theory of linear filter, ‘naive’ forecasting, exponential smoothing, stationary stochastic processes, optimal linear forecast, ARMA-processes, the autocorrelation function, model identification and parameter estimation in the time domain, among others.</p>
  </div>
  <div class="sec" id="section3">
  <h3>ME6: Applied Econometrics</h3>
  <p class = "text_ml">
  ME6 includes courses that focus on the application of advanced econometric methods to selected economic problems whereby emphasis is typically set on acquisition, processing and analysis of real datasets. In many courses, participants acquire in-depth knowledge in statistical programming.
  <ul>
	<li>Econometric Analysis Electricity and Financial Markets</li>
	<li>Applied Time Series Analysis in Macroeconometrics</li>
	<li>Topics in Economic Policy Evaluation</li>
	<li>Microeconometrics in Health Economics</li>
	<li>Econometric Applications in Monetary Economics</li>
  </ul>
  </p>
  </div>
  <div class="sec" id="section4">
  <h3>Electives</h3>
  <p class = "text_ml">
  Participants acquire knowledge about current theoretical developments in micro- or macroeconomics, applied econometrics and econometric methods by attending selected courses from blocks <b>ME5: Economics</b>, <b>ME6: Applied Econometrics</b> and <b>ME7: Econometric Methods</b>. Focus lies on the discussion, adaptation and application of various econometric tools on the one hand and on advanced and up-to-date topics of economic interest on the other hand.
.</p>
  </div>
  <div class="sec" id="section5">
  <h3>ME5: Economics</h3>
  <p class = "text_ml">
  Many econometric methods have been developed in line with developments in economics. Therefore, it is important for our students to be familiar with more recent theoretical developments and thus potential areas of application of econometric methods. Depending on the field of interest, the courses have a micro- or macroeconomic orientation. The curriculum covers a variety of courses from the following disciplines: 
  <ul>
	<li>Applied Macro- and Microeconomics</li>
	<li>Dynamic Macroeconomics</li>
	<li>Game Theory</li>
	<li>Health Economics</li>
	<li>Public Economics</li>
	<li>Financial Economics</li>
  </ul>
  </p>
  </div>
  <div class="sec" id="section6">
  <h3>ME7: Econometric Methods</h3>
  <p class = "text_ml">
  Modules in ME7 have a strong methodological orientation, i.e. students have the opportunity to acquire in-depth knowledge of econometric methods in selected fields, for example:
  <ul>
	<li>Stochastic Processes</li>
	<li>Unit Root and Cointegration Analysis</li>
	<li>Analysis of Big Data and Machine Learning</li>
	<li>Bayesian Econometrics</li>
	<li>Multivaruate Statistical Methods</li>
	<li>Advanced Microeconometrics</li>
  </ul>
  </p>
  </div>
  <div class="sec" id="section7">
  <h3>ME1: Statistical Theory</h3>
  <p>
  <p class = "text_ml">
  Participants learn to use the formal language of statistics und gain knowledge of fundamental concepts in stochastic, decision theory and asymptotic theory which are required in order to analyze, apply and further develop statistical procedures.
  <br>
  <br>
  ME1 consists of the following courses:
  </p>
  <p class = "tab"><b>_ Probability Theory (ME1a)</b></p> 
  <p class = "text_ml">
  An introduction to measure theory and stochastics necessary to formalize the questions discussed in statistical theory.
  </p>
  <p class = "tab"><b>_ Decision Theory (ME1b)</b></p>
  <p class = "text_ml">
  Introduces the basic concepts associated with statistical tests.
  </p>
  <p class = "tab"><b>_ Probability Theory (ME1c)</b></p>
  <p class = "text_ml">
  Deals with asymptotic properties of statistical methods and presents various central limit theorems used in statistics.
  </p>
  </p>
  </div>
  <div class="sec" id="section8">
  <h3>ME2: Econometrics</h3>
  <p class = "text_ml">
  ME2 deals with a wide range of fundamental econometric methods. Special emphasis is placed on asymptotic results to allow for a general discussion of the statistical properties of these methods. The main focus lies on a formally precise description of the concepts. Topics include the linear regression model, the generalized linear regression model, maximum likelihood estimation and inference, asymptotic theory, endogenous regressors, instrumental variables, generalized method of moments and regression models for time series data, among others.</p>
  </div>
  <div class="sec" id="section9">
  <h3>ME3: Case Studies</h3>
  <p class = "text_ml">
  The participants solve statistical problems in larger group projects, usually using raw economic data. They are trained in applied research and acquire skills in presenting statistical results and various interdisciplinary qualifications such as teamwork and know-how in project management, communication and consulting. Furthermore, students expand their methodological knowledge and gather experience in statistical programming.</p>
  </div>
<div class="sec" id="standarddiv">
<h3>Overview</h3>
<p class = "text_ml">The four-semester master's program in econometrics is devided into compulsory modules, elective courses and closes with the master thesis. In four compulsory modules (ME1 - ME4) with a total amount of 43 credit points, you acquire a sound knowledge in  statistics, econometrics and time series analysis. The core curriculum also conveys skills in applied research, statistical programming, research project management and statistical consulting. 
<br>
<br>
Elective modules (ME5 - ME6) train students in economic theory (ME5) provide further specialization in applied (ME6) and theoretical econometrics (ME7). In ME6 and ME7, students focus on a specific field of research according to their individual preferences. This results in a flexible number of credits to be acquired by electives, which must, however, amount to a minimum of 11 and a maximum of 25 credit points in each of the elective module areas. 
<br>
<br>
While core modules and many electices are taught in English, students have the opportunity to attend selected German-language courses.
<br>
<br>
Further information on the individual course areas can be viewed by clicking in the interactive semester plan above. Please note that the above plan is for orientation only. Students are free to decide in which order they complete core courses and elective modules. 
<br>
<br>
Details of all courses currenlty offered can be found in the following table. Please note that this list will be updated regularly.
</p>
</div>
</div>

````{r, echo = F}
Kurse <- read_xlsx("KurseMscECMX.xlsx", skip = 3, sheet = "Kurslisten") %>%
  distinct(Kurs, Ort, .keep_all = T) %>% 
  mutate(Course = paste("<a href='", 
                        `Link aktuelle Veranstaltungsübersicht`, 
                        "'>", 
                        Kurs,
                        "</a>", 
                        sep = "")) %>% 
  rename(Location = Ort)

# Set a coming soon text for courses without URL
Kurse[is.na(Kurse$`Link aktuelle Veranstaltungsübersicht`),] <- 
  Kurse[is.na(Kurse$`Link aktuelle Veranstaltungsübersicht`),] %>% 
  mutate(Course = paste(Kurs, "<br> New course! Page is coming soon.", 
                        sep = "")) 

Kurse[Kurse$Modulname == "Fortgeschrittene Ökonometrie",] <- 
  Kurse[Kurse$Modulname == "Fortgeschrittene Ökonometrie",] %>% 
  mutate(Course = paste("<a href='", `Link aktuelle Veranstaltungsübersicht`, 
                        "'>", Kurs,"</a>","<br> Part of the module 'Advanced Econometrics'", sep = ""))

# Set flag symbols
Kurse$Sprache[Kurse$Sprache == "deutsch"] <- "🇩🇪"
Kurse$Sprache[Kurse$Sprache == "englisch"] <- "🇬🇧"
Kurse$Sprache[Kurse$Sprache == "deutsch/englisch"] <- "🇩🇪🇬🇧"

Kurse <- Kurse %>% select(Course, Location, Section, Sprache) %>% rename(Language = Sprache)

kable(Kurse, escape = F, table.attr = 'id=\"table_id\"') %>%
  kable_styling(full_width = T, 
                bootstrap_options = c("striped", "hover", "responsive")) %>%
  column_spec(1, bold = T, border_right = F, width = "25em") %>%
  column_spec(2, border_right = F)
```
